### 2025-05-22 README.Rmd
update paper link to VeriXiv preprint

Ryan, G.E., Tierney, N., Golding, N., and Weiss, D.J (2025). [traveltime: an R package to calculate travel time across a landscape from user-specified locations](https://doi.org/10.31223/X56M74){target="_blank"}. **EarthArXiv** 10.31223/X56M74

>>>>

**Ryan, G.E.**, Tierney, N., Golding, N., and Weiss, D.J (2025). [traveltime: an R package to calculate travel time across a landscape from user-specified locations](https://doi.org/10.12688/verixiv.989.1){target="_blank"}. **VeriXiv** 2:99 DOI 10.12688/verixiv.989.1
